\documentclass[12pt]{article}
\usepackage[left=1.0in,right=1.0in,top=1in,bottom=1.0in]{geometry}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{fancyhdr,times}
\usepackage{pagecounting}
\usepackage{color}
\usepackage{setspace}
\singlespacing
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\usepackage{titlesec}
\titlespacing\section{0pt}{0pt}{0pt}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
 
\urlstyle{same}

\setlength{\parindent}{0em}
\setlength{\parskip}{0.75em}

\begin{document}
%\raggedright
%\setlength{\parindent}{6mm}
\pagestyle{fancy}
%\lhead{{\it Jason Marshall}}
\chead{{\Large \bf CALTECH RESOURCES}}
\rhead{{\thepage/\totalpages{}}}
\cfoot{}
\vspace*{-0.35in}

\textbf{Staff and Faculty Consultation Center (SFCC) -}\\
The SFCC is staffed by skilled mental health professionals with extensive experience in assisting employees and their families to balance the complex demands of work and personal life.  
Individual, couple, and family consultations are available to address a variety of concerns, including depression, anxiety, substance abuse, parenting, elder care, work-related stress, and communication challenges with supervisors, employees, or co-workers.
\url{https://sfcc.caltech.edu/} (626) 395-8360

\rule{\textwidth}{0.5pt}

\textbf{Caltech Center for Diversity (CCD) -}\\ 
The Caltech Center for Diversity's mission is to provide education, advocacy, and allyship in order to increase institutional and personal capacity for diversity, ensuring a community committed to equity and inclusive excellence. 
We create and implement campus-wide initiatives and programs that will increase the knowledge, skills, and attitudes for all members of the Caltech community to thrive in a diverse world.
\url{https://diversitycenter.caltech.edu/} (626) 395-6207

\rule{\textwidth}{0.5pt}

\textbf{Caltech Recreation Facilities -}\\
The mission of the Department of Athletics, Physical Education, and Recreation is to develop the physical, social, and emotional skills for people at Caltech necessary for the cultivation of a sound mind in a sound body. The Department seeks to encourage participation in a balanced program of individual and group activities through a variety of intercollegiate, physical education, club, intramural, and informal recreation activities intended to meet the needs of all members of the community.
\url{http://www.gocaltech.com/Recreation/index}

\rule{\textwidth}{0.5pt}

\textbf{Center for Teaching, Learning, \& Outreach (CTLO) -}\\
The Center for Teaching, Learning, \& Outreach supports Caltech's multifaceted educational efforts, including undergraduate and graduate courses and curricula, formal and informal learning, and partnerships with K-12 teachers and students.
\url{https://www.teachlearn.caltech.edu/}

\rule{\textwidth}{0.5pt}

\textbf{Caltech Career Development Center (CDC) -}\\
The Career Development Center is committed to assisting our Caltech undergraduate students, graduate students, and postdocs with career planning, including career exploration, graduate and professional school advising and job search strategies for full-time employment, internships and related opportunities.
\url{https://www.career.caltech.edu/}

\rule{\textwidth}{0.5pt}

\textbf{Disability Services at Caltech -}\\
Caltech welcomes and encourages employees with disabilities to reach out to the appropriate contacts for help with accomodations.  We are committed to a diverse community and provide reasonable accommodations so that those with disabilities can take advantage of the many opportunities Caltech has to offer.
\url{https://disability.caltech.edu/} (626)-395-5740

\textbf{Caltech Alumni Association (career resources) -}\\
The mission of the Caltech Alumni Association is to promote the interests of Caltech as a world standard of academic excellence by strengthening the ties of goodwill and communication between the institute, its alumni, and its students, and by maintaining programs to serve their needs.
\url{http://www.alumni.caltech.edu/careers/}

\rule{\textwidth}{0.5pt}

\textbf{Hixon Writing Center -}\\ 
The Hixon Writing Center (HWC) at the California Institute of Technology promotes excellence in writing and communication. The HWC operates on the premise that writing is a mode of discovery and learning as well as a tool for communication, and thus strong writing skills are fundamental to learning and success across disciplines. We pursue excellence in writing and communication through working actively with Caltech students, faculty, and the Caltech community.
\url{https://writing.caltech.edu/}

\rule{\textwidth}{0.5pt}

\textbf{Caltech International Spouses Club (CISC) -}\\
Open to spouses and partners of Caltech students, postdocs and JPL scientists with international backgrounds.  We are from different cultures and speak different languages, but share similar experiences of working to make Pasadena our new home. In CISC, we share our interests, cultures, life experiences, adventures, and even our grandmothers' recipes!  We help each other with information and nurture our friendships to overcome the difficulties of living in a foreign country to create fulfilling lives for ourselves and our families. If you find yourself alone while your spouse is busy studying or working, you are warmly welcomed to join the fun we have here at CISC.
\url{https://international.caltech.edu/CISC}


\end{document}

